% latex table generated in R 4.4.1 by xtable 1.8-4 package
% Wed May 21 19:45:16 2025
self\_cited\_count & what.reviewer.said \\ 
  \hline
  3 & Also, the introduction, main discussion, and conclusion must be redrawn to highlight NO as a treatment option, the clinical trials discussion, the use of several NORMS (NORM-1, NORM-2, etc), the effect of NO-carriage system, Natural NO-sources, synthetic NO-sources with limitations, Inorganic versus organic forms, etc (eg., in the review publications as given \\ 
    1 & The term 'true bugs' applies to the monophyletic Heteroptera, which does include the species presented here (Acanthosoma haemorrhoidale), while aphids and mealybugs belong to the distinct lineage Sternorrhyncha, sometimes (formerly) regarded as a part of the paraphyletic Homoptera (see, for example, Figure 2 in: [xxxx]). \\ 
    1 & On a side note: There is already published work on population genomics of the European plaice showing that two large chromosomal rearrangements (two putative inversions) segregate in northern plaice populations (North Sea, Baltic Sea, Barents Sea, and Iceland) and distinguish different plaice populations. \\ 
    1 & There is some observational clinical data on how the detrusor compensates for the growing prostate and the-by consequence-increase in bladder outflow obstruction, in addition to the animal studies referred to in the commentary, to explain the pathophysiology. \\ 
    1 & I would like to thank the authors for including references to the work done in the [xxxx] project; I would recommend to remove the reference ([xxxx] et al., 2019b) and replace it with a reference to a much more recent and related paper (xxxx et al.): \\ 
    2 & The cited literature is incomplete; it does not include all reports of studies on the presence of the snail in Colombia, and studies with relevant findings of nematodes with or without pathogenic potential in animals are omitted e.g: \\ 
    1 & In the last 2 decades, our group has developed a brief instrument to assess the presence and the severity of sensory phenomena (the University of [xxxx]) to investigate OCD phenotypic subtypes and its relationship with TS/CTD. \\ 
    5 & The authors can find the following relevant articles to enhance their Materials and Methods section and incorporate citations to support their revised manuscript. \\ 
    3 & The authors should consider references from high impact journal publications on crop yield prediction. For example, the following articles by this reviewer \\ 
    1 & No mention to more rigorous rankings such as the Leiden Ranking are made nor to what exactly rankings are portraying. See for instance [xxxx]. \\ 
    1 & Maybe 'manifest' and 'not manifest' would work better [for example we used this terminology in [xxxx]. \\ 
    1 & This is especially useful if you have multiple data sets - see, for example, the [xxxx] package. \\ 
    3 & I would suggest the authors include some of the results of a large-scale project in Europe. \\ 
    2 & Please refer to some further references to revise the relevant description: \\ 
    1 & Here are a few additional publications you might consider referencing. \\ 
    1 & However, genomics resources are limited, except for parasitoid wasps. \\ 
    1 & Refer to this recent literature review. \\ 
    4 & No relevant sentence \\ 
    1 & No relevant sentence \\ 
    6 & No relevant sentence \\ 
  